---
title: "Untitled"
format: html
editor: visual
---

```{r warning=FALSE, message=FALSE}
# Packages
library(readr)
library(tidyverse)
library(dplyr)
library(stringr)
library(RSelenium)
```

```{r warning=FALSE, message=FALSE}
# Loading data
X5201_data <- read_csv("~/Downloads/Altmetric - Research Outputs - London School of Economics and Political Science - 2024-10-24.csv")
X5202_data <- read_csv("~/Downloads/Altmetric - Research Outputs - London School of Economics and Political Science - 2024-10-24 (4).csv")
X5203_data <- read_csv("~/Downloads/Altmetric - Research Outputs - London School of Economics and Political Science - 2024-10-24 (3).csv")
X5204_data <- read_csv("~/Downloads/Altmetric - Research Outputs - London School of Economics and Political Science - 2024-10-24 (1).csv")
X5205_data <- read_csv("~/Downloads/Altmetric - Research Outputs - London School of Economics and Political Science - 2024-10-24 (2).csv")

```

## Binding Dataframes

Because of the sheer number of academic articles, we've had to import them in five seperate files. We're going to bind these together into one big dataframe.

```{r}
altmetrics_data <- bind_rows(X5201_data, X5202_data, X5203_data, X5204_data, X5205_data)
```

There is some overlap between the datasets, so we'll remove duplicates.

```{r}
altmetrics_data <- distinct(altmetrics_data)
```

```{r}
head(altmetrics_data)
```

**What is included in this data:**

-   All article publications in the category 'psychology' listed on Dimensions.ai database.

**What isn't included:**

-   Books

-   Book chapters

-   Data sets

-   Clinical trial records

-   News stories

**What information do we get on each source**

-   Impact measure: altmetrics

    -   Overall altmetrics score

    -   News mentions

    -   Blog mentions

    -   Policy mentions

    -   Patent mentions

    -   X mentions

    -   Peer review mentions

    -   Weibo mentions

    -   Facebook mentions

    -   Wikipedia mentions

    -   Google+ mentions

    -   LinkedIn mentions

    -   Reddit mentions

    -   Pinterest mentions

    -   F1000 mentions

    -   Q&A mentions

    -   Video mentions

    -   Sllyabi mentions

    -   Number of mendeley readers

    -   Number of citations

-   Article title

-   Journal title

-   Open access status

-   Subject categories

-   Publication date

-   Publisher names

**What info do we not get on each source?**

-   Citation-based impact metrics other than the number of citations (e.g. RCR or CNCI).

-   Usage-based impact metrics (e.g. page views or downloads)

**How can we compensate for this?**

-   Altmetric explorer API

```{r}
names(altmetrics_data)
```

**Quantification of impact**

-   Policy mentions

-   Social media mentions (combined facebook, linkedin reddit, x)

-   News mentions

-   Patents

-   Citations

-   Altmetrics
